Proposal to improve BBC Search through the use of Linked Data

### 2014-05-05 chapter1.tex
Drawing a line under chapter 2 for now so I can move on to the important stuff. I've not said anything around inference, but I probably don't need to.

The Search application needs to read in or receive metadata about
BBC content from a variety of sources and then needs to serve
a diverse set of use cases.\cite{fenning2014applicability} The
need to integrate against different data sources and funnel
that information into a common set of search indexes can
typically be seen as an \emph{enterprise integration}
problem. Architectural patterns have been developed, tested and
implemented in a large number of enterprises to synchronise,
transform and normalise data. Such patterns are notably
summarised by Hohpe and Woolf.\cite{hohpe2004enterprise}

@@

The current BBC Search application returns an ordered list of results
for queries based on keyword matching within the titles, text or other
chosen metadata fields as appropriate. However, there are cases where
the algorithms employed may not return something noted as the official
or canonical match for a concept, person, programme, etc. (e.g. the
official microsite for a popular BBC programme or a profile page for
a notable person on BBC News).

>>>>

The Search application needs to read in or receive metadata about
BBC content from a variety of sources and then needs to serve
a diverse set of use cases.\cite{fenning2014applicability} The
need to integrate against different data sources and funnel
that information into a common set of search indexes can
typically be seen as an \emph{enterprise integration}
problem.

@@

`The current BBC Search application returns an ordered list of results
for queries based on keyword matching within the titles, text or other
chosen metadata fields as appropriate. However, there are cases where
the algorithms employed may not return something noted as the official
or canonical match for a concept, person, programme, etc. (e.g. the
official microsite for a popular BBC programme or a profile page for
a notable person on BBC News).

### 2014-05-05 chapter2.tex
Drawing a line under chapter 2 for now so I can move on to the important stuff. I've not said anything around inference, but I probably don't need to.

In recent years, a growing trend has emerged to use
\emph{Linked Data} in the enterprise to remove the need
for repeated integration projects or data warehousing.
\cite{allemang2010semantic} If we view the indexing processes
of a search application as a variant of data warehousing,
we can start to argue for enterprise-wide publishing of
linked data as a more cost effective means of building search
indexes over bespoke integration efforts.

@@

These efforts are not as structured and rich as the more notable uses
of semantic web technologies on the programmes microsites, Nature and BBC
Music \cite{raimond2010use}, but indicate that some level of metadata
can be retrieved
as linked data. In cases where the metadata are rich enough, it might be
possible to avoid direct integration with databases, hidden back end
web services and other structured ``feeds'' typically set up for enterprise
integration.

\section{Reasoning and Inference}
\label{reasoning}

>>>>

\emph{Enterprise integration} is an important technical field within the
discipline of Enterprise Architecture that focuses on interconnecting
systems and allowing data to flow between them. This can be seen as
the practice of breaking down information silos that naturally emerge
in enterprise organisations.\cite{allemang2010semantic}

Architectural patterns have been developed, tested and
implemented in a large number of enterprises to synchronise,
transform and normalise data. Such patterns are notably
summarised by Hohpe and Woolf.\cite{hohpe2004enterprise}

There are difficulties with some of these approaches noted by
Allemang\cite{allemang2010semantic}. Data warehousing,
integration projects and metadata repositories can all
be time-consuming to implement, require repeated updating when
use cases change and at the extreme can be seen as solving the
problem of too many silos by adding another silo.

In recent years, a growing trend has emerged to use
Linked Data in the enterprise to remove the need
for repeated integration projects or data warehousing.
indexes over bespoke integration efforts. This follows from
a major motivation of Linked Data being that it aids in breaking
down information silos. \cite{bizer2009linked} In the
\emph{Linked Enterprise Data} approach, all information
production remains \emph{distributed} but is
\emph{connectable}.\cite{allemang2010semantic}

An organisation that seeks to ensure that all information is
published as Linked Data can learn from examples such as Wikipedia
-- or indeed the web in general -- where individual experts are
encouraged to share knowledge rather than keep it in silos. This
distributed approach recognises that diversity and flux are the
steady state of an agile enterprise. Two sources that happen
to use the same vocabulary are instantly interoperable. Two
sources that use a different vocabulary could well be integrated
simply by creating appropriate mappings between the vocabularies.
It should not be necessary to re-engineer a whole dataset nor
create entirely new systems just for integration.

There are still costs however in additional services, infrastructure
and training in exposing data as linked data throughout the
enterprise.\cite{hyland2010preparing} A practical approach
has been suggested by Davis\cite{davis2011achieving} where enterprises
can expose data via known formats such as Atom\cite{nottingham2005atom}
and RESTful web services. Davis argues that the \texttt{atom:link}
element offers some of the functionality of an RDF triple where
an entity can be linked to other entities via the \texttt{href}
attribute and the nature of that relationship is described by
the \texttt{rel} attribute.

The use of RESTful services and XML formats are very common in
the enterprise -- noting however that many do not follow all tenets
of the REST architectural style. This suggests that businesses
could adopt the pattern suggested by Davis to expose their
data across the organisation using technologies and techniques
with which they are likely familiar. This eschews the full power
of a stack based RDF, OWL and SPARQL, but might be a better
opportunity for businesses that otherwise would not take on a
Linked Data approach at all.  Many proponents of Linked Data would
argue that the important aspect is that the data are exposed and
linked, however that is achieved.

\begin{comment}
If we view the indexing processes
of a search application as a variant of data warehousing,
we can start to argue for enterprise-wide publishing of
linked data as a more cost effective means of building search

@@

These efforts are not as structured and rich as the more notable uses
of semantic web technologies on the programmes microsites, Nature and BBC
Music \cite{raimond2010use}, but indicate that some level of metadata
can be retrieved
as linked data. In cases where the metadata are rich enough, it might be
possible to avoid direct integration with databases, hidden back end
web services and other structured ``feeds'' typically set up for enterprise
integration.
\end{comment}
